The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-03-20 paper/ms.tex
tim edits

We can assess the importance of this contamination by considering differences between quarters. Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars are observed on different CCD modules with the exception of stars on the central Module~13. Minor variations in the precise alignment of each CCD mean that the contribution from contaminating stars varies from quarter to quarter. Differences are clearer for Module~13, where contaminating stars will only be aligned along the same columns as a smear target every second quarter. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers. We consider only odd and even quarters separately, and also the full combined time series. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In order to better quantify this, we computed the inner product of normalized periodograms of the odd and even quarters, each smoothed with a 3-element Gaussian kernel. If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons. We found that the distribution of overlaps (Figure~\ref{contamination2}) is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$. We investigate these further, finding that in some of these cases  there was no obvious problem. For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical.

@@

Several stars in the sample show the `hump-and-spike' morphology in their power spectra \citep[][a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band]{2013MNRAS.431.2240B,2014MNRAS.441.3543B,2017MNRAS.467.1830B,2018MNRAS.474.2774S}: these are marked `H+S' in Table~\ref{stellar_props}.
%HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. 
Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect. The identification for HD~189178 is tentative, as the spectrum also shows evidence of SPB pulsations, and for HD~183362 for $\gamma$\,Dor pulsations, while for HD~184787 there is long term variability consistent with contamination. The other hump-and-spike identifications seem secure. \citet{2018MNRAS.474.2774S} have recently interpreted the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main-sequence. A detailed study of these stars will be presented by Antoci et al., in prep.

>>>>

We can assess the importance of this contamination by considering differences between quarters. Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars were observed on different CCD modules with the exception of stars on the central Module~13. Minor variations in the precise alignment of each CCD mean that the contribution from contaminating stars varies from quarter to quarter. Differences are clearer for Module~13, where contaminating stars will only be aligned along the same columns as a smear target every second quarter. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers. We consider only odd and even quarters separately, and also the full combined time series. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In order to better quantify this, we computed the inner product of normalized periodograms of the odd and even quarters, each smoothed with a 3-element Gaussian kernel. If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons. We found that the distribution of overlaps (Figure~\ref{contamination2}) is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$. We investigate these further, finding that in some of these cases  there was no obvious problem. For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical.

@@

Several stars in the sample show the `hump-and-spike' morphology in their power spectra \citep[a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band;][]{2013MNRAS.431.2240B,2014MNRAS.441.3543B,2017MNRAS.467.1830B,2018MNRAS.474.2774S}: these are marked `H+S' in Table~\ref{stellar_props}.
%HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. 
Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect. The identification for HD~189178 is tentative, as the spectrum also shows evidence of SPB pulsations, and for HD~183362 for $\gamma$\,Dor pulsations, while for HD~184787 there is long term variability consistent with contamination. The other hump-and-spike identifications seem secure. \citet{2018MNRAS.474.2774S} have recently interpreted the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main-sequence. A detailed study of these stars will be presented by Antoci et al., in prep.
